What does it take to create with domain-appropriate tools?

### 2020-01-22 convivial-2020/tex/manuscript.tex
DONE

\documentclass[english,submission]{programming}
\usepackage[backend=biber]{biblatex} % Use Biblatex
\addbibresource{example.bib}

@@

\paperdetails{
  perspective=art,
  area={General-purpose programming}
}

\begin{CCSXML}
<ccs2012>
<concept>
<concept_id>10002944.10011122.10003459</concept_id>
<concept_desc>General and reference~Computing standards, RFCs and guidelines</concept_desc>
<concept_significance>300</concept_significance>
</concept>
</ccs2012>
\end{CCSXML}

\ccsdesc[300]{General and reference~Computing standards, RFCs and guidelines}`

@@

\acks
I want to thank ....

>>>>

\documentclass[english,submission]{programming}
\usepackage[
backend=biber,
style=alphabetic
]{biblatex} % Use Biblatex
\addbibresource{../refs.bib}

@@

\paperdetails{
  perspective=art,
  area={Domain-specific programming, visual programming, self-sustaining systems}
}

\begin{CCSXML}
<ccs2012>
   <concept>
       <concept_id>10011007.10011006.10011050.10011017</concept_id>
       <concept_desc>Software and its engineering~Domain specific languages</concept_desc>
       <concept_significance>500</concept_significance>
       </concept>
   <concept>
       <concept_id>10011007.10011006.10011050.10011058</concept_id>
       <concept_desc>Software and its engineering~Visual languages</concept_desc>
       <concept_significance>300</concept_significance>
       </concept>
 </ccs2012>
\end{CCSXML}

\ccsdesc[500]{Software and its engineering~Domain specific languages}
\ccsdesc[300]{Software and its engineering~Visual languages}

@@
